---
title: "DDP"
author: "Karthikeyan Ramakrishnan"
date: "Tuesday, October 21, 2014"
output: html_document
runtime: shiny
---

This is a simple user document to run price predication application of diamond price. 

This is built on shiny, based on simpe linear prediction. 

Input for this app is carat size, the same shall be entered by moving arrow keys.

```{r,echo=FALSE}
inputPanel(numericInput("cr","cr:",0.1,min=0.1,max=50,step=.25))
```

The corresponding output shall be as below column:

```{r,echo=FALSE,message=FALSE}

library(UsingR)
data(diamond)
renderPrint({
        fit<-lm(price~carat,data=diamond)
        predict(fit,newdata=data.frame(carat=input$cr))
          })

```

Plot for the graph as below, red dots represent the actual price wrt carat size, blue line represents regression line based on linear model.

```{r,echo=FALSE,warning=FALSE}
renderPlot({
  fit<-lm(price~carat,data=diamond)
        plot(diamond$carat,diamond$price,xlab="size of carat",ylab="Price",col="red")
        lines(diamond$carat,fit$fitted.values,col="blue")
      })


```

